Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-09-03 Ben_Manuscripts/Paper1/Outline.tex
Updated outline test.
Lots of comments.

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section*{Introduction}

@@

  A clear picture of the nanoscopic LLC membrane structure, gained by building 
  a molecular model will provide evidence to answer existing and newly proposed
  questions.
  \begin{itemize}
    \item We will limit our initial studies to studying assemblies formed by Na-GA3C11
    \item We have also chosen to focus our initial efforts on the development of 
    a model of the Col\textsubscript{h} phase membrane.
    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
    phase is a simpler starting point, due to the absence of water, and has
    equivalent experimental structural data.
    \item Despite having structural data, there is still information which 
    experiment cannot definitively answer
    \item The Col\textsubscript{h} phase is described as having pores made of
    disks or layers stacked on top of one another, each containing a set 
    number of monomers. A simple simulation study of a similar molecule suggests
    that there are 4 monomers in each disk~\cite{zhu_methacrylated_2006}. A 
    separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    A molecular model has the best chance of directly answering this question.
    \item Once we know the number of monomers in each layer, we still do not know how 
    monomers in each layer are positioned with respect to other layers. 
    \item A driving force of self assembly in this system is thought to be pi-pi
    stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
    \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
    advantage for parallel displaced and T-shaped pi-pi stacking conformations versus a
    sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
    \item Substituted benzene rings exhibit an even stronger pi-pi stacking 
    attraction which favors the parallel displaced configuration in all cases
    except where the substitutions are extremely electron withdrawing
    \cite{waller_hybrid_2006,ringer_effect_2006}.
    \item While we might be able to provide answers to these questions using a 
    molecular model, there remains the possibility that there is more than one 
    metastable state associated with a given LLC system.
    \item We must be able to identify which states can be produced experimentally
    and what implications each state might have regarding transport properties.
  \end{itemize}

  A molecular level understanding of LLC membrane structure will provide guidelines
  to reduce the large chemical space available to design monomers for creation of 
  separation-specific membranes.
  \begin{itemize}
%     \item LLCs are versatile and controllable with a \textbf{large chemical design
%     space} available for membrane design  %BJC: redundant
    \item  We do not yet understand how to reduce the effective pore size or 
    how to tune the chemical environment in the nanopores for effective water
    desalination or small organic separations.
    \item Rejection studies show that this membrane can not perform separations of
    solutes less than 1.2 nm because the pores are too large \cite{zhou_supported_2005}.
    \item Over the past 20 years, LLC membrane studies have been limited primarily 
    to Na-GA3C11 with some characterization done after minor structural modifications
    \cite{resel_structural_2000}. 
    \item Optimization has been performed through trial and error. The only source of 
    predictive modeling has been macroscopic models which likely do not adequately describe 
    transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
    \item It will be challenging to efficiently narrow down the design space in 
    a laboratory setting.
    \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
    structure which will be crucial to understanding the role of monomer structure in 
    membrane design.
    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
    \item Choice of counterion may influence the establishment of a Donnan potential 
    affecting the degree to which the membrane can exclude charged species.
    \item Moieties inside the pores may interact with neutral solutes, rejecting
    on the basis of shape and size, rather than just hydrodynamic radius.
    \item  An atomistic understanding of pore structure and its influence on transport 
    is necessary to identify performance bottle necks and direct design of future membranes. 
  \end{itemize}

  We must show that the developed molecular model is consistent with
  physical observations so that we can rely on conclusions drawn about % better word for trust?
  structural features characteristic of the system.
  \begin{itemize}
    \item This article will illustrate the development of a predictive molecular model 
    and the steps taken to ensure it mimics the real system within the constraints 
    inherent to MD.
    \item To understand how physically realistic the model is, validation by comparison
    to experiment is necessary. We are primarily interested in reproducing the 
    conclusions about structure which have been made from X-ray diffraction (XRD) 
    experiments and in matching ionic conductivity measurements~\cite{feng_thin_2016}.
    \item We have comparied simulated X-ray diffraction patterns to experiment in 
    order to match major features present in the 2D patterns.
    \item We calculated ionic conductivity using two agreeing methods.
    \item We examined the the influence of crosslinking on membrane structure.
    \item We have created a model that can be used to probe the large design space
    available for membrane design
    \item The analysis used in this paper can be readily extended to the H\textsubscript{II}
    phase and other similar LC systems.
  \end{itemize}

@@

  An ensemble of characteristic, low-energy vacuum monomer configurations
  were constructed by applying a simulated annealing process to a
  parameterized monomer.
  \begin{itemize}
    \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
    \item A low energy configuration was pulled from the trajectory 
    and charges were reassigned using the am1bccsym method of molcharge
    shipped with Openeye Scientific software's QUACPAC % BJC: how to cite?
    \item Using the new charges, the monomer system was annealed again and monomer
    configurations were pulled from the trajectory to be used for full
    system construction (Figure~\ref{fig:python}a).
  \end{itemize}

  The timescale for self assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic
  simulation, calling for a more efficient way to build the system. 
  \begin{itemize}
    \item Previous work has shown a coarse grain model self assemble into
    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
    \item We attempted atomistic self-assembly by packing monomers into a box 
    using Packmol \cite{martinez_packmol:_2009}.
    \item Simulations of greater than 100 ns show no indicators of progress 
    towards an ordered system.
    \item To bypass the slow self-assembly process, python scripts are used
    to assemble monomers into a structure close to the expected equilibrium 
    configuration (Figure~\ref{fig:python}).
    \item A short, restrained equilibration, followed by NPT simulations 
    between 400 and 500 ns, allows the initial configuration to relax into
    an equilibrium configuration.
    \item Our logic for choosing a starting configuration and the details 
    of the equilibration schemes are presented below.
  \end{itemize}

  \begin{figure}[h]
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
  \end{figure}

  A typical simulation volume contains four pores in a monoclinic unit cell,
  the smallest unit cell that maintains hexagonal symmetry when extended 
  periodically.
  \begin{itemize}
    \item Each pore is made of twenty stacked monomer layers with periodic 
    continuity in the z direction, avoiding any edge effects and creating an 
    infinite length pore ideal for studying transport.
    \item A small number of layers is preferred in order to reduce computational
    cost and to allow us to look at longer timescales.
    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
    This point will be explained in more detail later.
  \end{itemize}

@@

@@

@@

@@

    a perfect hexagonal array. Only 4 are independent  %BJC: small figure here for clarity? supplemental info?

@@

@@

    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom apart.

@@

@@

@@

@@

    its $\approx$ 5 \angstrom equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.

@@

@@

  An equilibration scheme with position restraints placed on aromatic rings
  prevents unrealistic jumps during early equilibration steps.
  \begin{itemize}
    \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
    configurations while allowing monomer tails to settle.
    \item Doing so also mitigates system dependence on initial monomer configuration.
    \item Restrained equilibrations are run in the NVT ensemble.
    \item Every 50 ps, we reduce the force constants by the square root of its 
    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
    restraining potential.  %BJC: I can reference an equilibration script that can be released with the supplemental info or something
    \item The resulting unrestrained structure is allowed to equilibrate in the NPT
    ensemble for 400 - 500 ns.
  \end{itemize}

  %BJC: the following paragraph will be replaced with something that Joe writes
  Simulated X-ray diffraction patterns were generated based on atomic
  coordinates for a direct experimental comparison.
  \begin{itemize}
    \item All atomic coordinates were simulated as gaussian spheres of electron
    density corresponding to each atom's atomic number.
    \item A three dimensional fourier transform (FT) of the array of electron 
    density results in a three dimensional structure factor which represents
    the unit cell in reciprocal space.
    \item We perform an angular average of the structure factor about the 
    z axis to generate a 2D cross section close to what one would see 
    experimentally.
    \item We matched experimental 2D WAXS patterns by iterative improvement
    of our choice of initial structure and equilibration procedure.
  \end{itemize}

  \begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom apart. (b) Parallel-Displaced benzene dimers stack
	3.4 \angstrom vertically and 1.6 \angstrom horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom apart. 
	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
	configuration }\label{fig:stacking}
  \end{figure}

  Ionic conductivity was calculated using two different methods for
  robustness.
  \begin{itemize}
    \item The Nernst-Einstein relation relates the DC ionic conductivity to 
    ion diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann 
    constant, $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$  %BJC: need citation
    \item Sodium ion diffusion coefficients were found by calculating the slope
    of the linear region of the mean square displacement curve as indicated by
    the einstein relation \cite{einstein_investigations_1956}.]
    \item Ion concentration was measured with respect to the entire unit cell. %BJC: I don't think this needs to be said
    \item The second method, termed the 'Collective Diffusion' model, measures 
    the movement of the collective variable, Q, which is defined as the amount
    of charge transfer through the system.
    \item The diffusion coefficient of Q, $D_Q$, can be calculated using the 
    einstein relation.
    \item The conductance, $\gamma$ of the system can be calculated as:
    $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
    achieved by multiplying by channel length and dividing by the membrane
    cross sectional area.
    \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.
  \end{itemize}

  Using an equilibrated structure, a crosslinking procedure was performed
  in order to better parallel synthetic procedures. 
  \begin{itemize}
    \item The purpose of crosslinking is to maintain macroscopic alignment of 
    the crystalline domains, ensuring aligned, hexagonally packed pores.
    \item For that reason, we are not concerned with replicating the kinetics 
    of the reaction, but instead emphasize the consistency of the final structure
    with experimental structural data.
    \item The algorithm was developed based on the known reaction mechanism.
    \item Crosslinking of this system is a free radical polymerization (FRP)
    taking place between terminal vinyl groups present on each of the three
    monomer tails.
    \item FRPs require an initiator which bonds to the system, meaning new atoms
    were introduced into the system.
    \item For simplicity, the initiator was simulated as hydrogen and made present 
    in the simulation by including them in all possible bonding positions as dummy atoms.
    \item The crosslinking procedure is carried out iteratively.
    \item During each iteration, bonding carbon atoms are chosen based on a distance cut-off.
    \item The topology is updated with new bonds and dummy hydrogen atoms are 
    changed to appropriate hydrogen types. 
    \item Head-to-tail addition was the only propagation mode considered due to 
    its dominance the real system.
    \item Direction of attack was not considered because the resultant mixture 
    is racemic.
    %BJC: The following items belongs in results/discussion
    \item The resulting crosslinked structure has an even distribution of
    crosslinks between monomer tails of the same monomer, monomers stacked on
    top of each other and monomers in other pores, including across periodic
    boundaries.
    \item The pore spacing shrinks by $\approx$ 1 \angstrom and stays 
    constant under a range of simulation conditions.
  \end{itemize}

@@

  To discern the composition of the monomer layers, we ran simulations of 
  systems created with 4 - 8 monomers per layer.
  \begin{itemize}
  	\item Both the sandwiched and parallel displaced configurations were tested.
	\item All systems remained stable for at least 50 ns.
	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
	Systems built with 5 monomers in each layer equilibrate to a pore spacing
	that is most consistent with the experimental value of 4.12 nm derived from
	SAXS measurements (Figure~\ref{fig:SAXS}).
	\item We verified that the system stays partitioned into layers by plotting 
	pair correlation functions calculated between aromatic rings along the length
	of the pores (Fig~\ref{fig:zdf}).
	\item The remainder of this discussion will focus on the analysis of systems
	built with 5 monomers per layer. 
  \end{itemize}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
%MRS: paper needs a conclusions section outlined.
%MRS: maybe replace pi with $\pi$,qz with $q_z$, and \angstrom by \angstrom~ (the tilde is an enforced space)
%MRS: also maybe \AA instead of \angstrom?  I can't remember which formats better in text.
%\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
%MRS: focus isn't really on transport, but on what the strucures are.
\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
%MRS: I don't know that we need to put MD simulations alone in the title, since we also do a fair amount of comparison to experiment. 
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joe Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
\begin{document}
  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}
  \maketitle
  \section*{Introduction}

@@

  A clear picture of the nanoscopic LLC membrane structure, gained by building 
  a molecular model will provide evidence to answer existing and newly proposed
  questions.
%MRS: break this down into more hierarchy - there are 11 separate points.  Can they be grouped at all for clearer understanding? elucidate what the aspects are we need a clearer picture. 
  \begin{itemize}
    \item We will limit our initial studies to studying assemblies formed by Na-GA3C11
    \item We have also chosen to focus our initial efforts on the development of 
    a model of the Col\textsubscript{h} phase membrane.
    \item Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
    phase is a simpler starting point, due to the absence of water, and has
    equivalent experimental structural data.
%MRS: since the questions we answer in the paper have a lot to do with the structure of the membranes, somewhere relatively early in the paper we need to lay out the facts that 1) these membranes could be really good (I think you do establish this) 2) we really would need to know the structure better to really do useful things with these, and 3) MD is a very helpful way to gain more information about the structure, because of the limited range of experiments we can do with these systems. That is the main rationale, and it should be made clear fairly early in the introduction.  Very important to make your story absolutely as clear as possible.
    \item Despite having structural data, there is still information which 
    experiment cannot definitively answer
    \item The Col\textsubscript{h} phase is described as having pores made of
    disks or layers stacked on top of one another, each containing a set 
    number of monomers. A simple simulation study of a similar molecule 
%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.  I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context. We thought they did something reasonable, but they really didn't. 
%suggests
suggested
    that there are 4 monomers in each disk~\cite{zhu_methacrylated_2006}. A 
    separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    A molecular model has the best chance of directly answering this question.
%MRS: phrasing
    %\item Once we know the number of monomers in each layer, we still do not know how 
    Even if we knew the number of monomers in each layer, we still would not know how 
    monomers in each layer are positioned with respect to other layers. 
    \item A driving force of self assembly in this system is thought to be pi-pi
    stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
    \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
    advantage for parallel displaced and T-shaped pi-pi stacking conformations versus a
    sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
    \item Substituted benzene rings exhibit an even stronger pi-pi stacking 
    attraction which favors the parallel displaced configuration in all cases
    except where the substitutions are extremely electron withdrawing
    \cite{waller_hybrid_2006,ringer_effect_2006}.
    \item While we might be able to provide answers to these questions using a 
    molecular model, there remains the possibility that there is more than one 
    metastable state associated with a given LLC system.
    \item We must be able to identify which states can be produced experimentally
    and what implications each state might have regarding transport properties.
  \end{itemize}

  A molecular level understanding of LLC membrane structure will provide guidelines
  to reduce the large chemical space available to design monomers for creation of 
  separation-specific membranes.
  \begin{itemize}
%     \item LLCs are versatile and controllable with a \textbf{large chemical design
%     space} available for membrane design  %BJC: redundant
    \item  We do not yet understand how to reduce the effective pore size or 
    how to tune the chemical environment in the nanopores for effective water
    desalination or small organic separations.
    \item Rejection studies show that this membrane can not perform separations of
    solutes less than 1.2 nm because the pores are too large \cite{zhou_supported_2005}.
    \item Over the past 20 years, LLC membrane studies have been limited primarily 
    to Na-GA3C11 with some characterization done after minor structural modifications
    \cite{resel_structural_2000}. 
    \item Optimization has been performed through trial and error. The only source of 
    predictive modeling has been macroscopic models which likely do not adequately describe 
    transport at these length scales. % BJC: Reference. I think it is just w.r.t. bicontinuous cubic
    \item It will be challenging to efficiently narrow down the design space in 
    a laboratory setting.
    \item A good molecular model should incorporate a detailed picture of the nanoscopic pore 
    structure which will be crucial to understanding the role of monomer structure in 
    membrane design.
    \item Choice of head group may play a role in the rejection of charged or uncharged solutes.
    \item Choice of counterion may influence the establishment of a Donnan potential 
    affecting the degree to which the membrane can exclude charged species.
    \item Moieties inside the pores may interact with neutral solutes, rejecting
    on the basis of shape and 
    %MRS: size pretty much is hydrodynamic radius
    %size, 
    interations with specific chemical groups
rather than just hydrodynamic radius.
    %MRS: isn't this next point just a restatement of what was said at the top?
    \item  An atomistic understanding of pore structure and its influence on transport 
    is necessary to identify performance bottle necks and direct design of future membranes. 
  \end{itemize}

  We must show that the developed molecular model is consistent with
  physical observations so that we can rely on conclusions drawn about % better word for trust?
  structural features characteristic of the system.
  \begin{itemize}
    %MRS: main finding shouldn't be the model, but the things learned from the model. New suggestion below.
    %\item This article will illustrate the development of a predictive molecular model 
    %and the steps taken to ensure it mimics the real system within the constraints 
    %inherent to MD.
    \item In this study, we build a significantly more realistic atomistic model of LLC membranes than has ever previously been done, and explore what new structural information can be gained and what structure hypotheses are supported by this model.

    %MRS: this is kind of understood -- rephrasing?
    %\item To understand how physically realistic the model is, validation by comparison
    to experiment is necessary. 
    \item We validate the model using as much experimental information as pissible.
    We are %primarily 
    most interested in reproducing the 
    conclusions about structure which have been made from X-ray diffraction (XRD) 
    experiments and in matching ionic conductivity measurements~\cite{feng_thin_2016}.
    %MRS: these are really supporting items to the above: put them indented.
    \item We have comparied simulated X-ray diffraction patterns to experiment in 
    order to match major features present in the 2D patterns.
    \item We calculated ionic conductivity using two agreeing methods.
    \item We examined the the influence of crosslinking on membrane structure.

    %\item We have created a model that can be used to probe the large design space
    available for membrane design
    \item The structure-building approach and analysis used in this paper can be readily extended to the H\textsubscript{II}
    phase and other similar LC systems.
  \end{itemize}

@@

  An ensemble of characteristic, low-energy vacuum monomer configurations
  were constructed by applying a simulated annealing process to a
  parameterized monomer.
  \begin{itemize}
    \item Monomers were cooled from 1000K to 50K over 10 nanoseconds.
    %MRS: how chosen?  randomly?  Be precise.  
    \item A low energy configuration was pulled from the trajectory 
    and charges were reassigned using the am1bccsym method of molcharge
    shipped with Openeye Scientific software's QUACPAC % BJC: how to cite?
    \item Using the new charges, the monomer system was annealed again and monomer
    configurations were pulled from the trajectory to be used for full
    system construction (Figure~\ref{fig:python}a).
  \end{itemize}

  The timescale for self assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic
  simulation, calling for a more efficient way to build the system. 
  \begin{itemize}
    \item Previous work has shown a coarse grain model self assemble into
    the H\textsubscript{II} phase configuration in $\approx$ 1000 ns \cite{mondal_self-assembly_2013}.
    \item We attempted atomistic self-assembly by packing monomers into a box 
    using Packmol \cite{martinez_packmol:_2009}.
    \item Simulations of greater than 100 ns show no indicators of progress 
    towards an ordered system.
    \item To bypass the slow self-assembly process, python scripts are used
    to assemble monomers into a structure close 
    %MRS:
    %to the expected equilibrium configuration. 
    one of a number of hypothesized equilibrium configurations (Figure~\ref{fig:python}).
    \item A short, restrained equilibration, followed by NPT simulations 
    between 400 and 500 ns, allows the initial configuration to relax into
    an equilibrium configuration.
    \item Our logic for choosing a starting configuration and the details 
    of the equilibration schemes are presented below.
  \end{itemize}

  \begin{figure}[!ht]
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and placed in a monoclinic unit cell}\label{fig:python}
  \end{figure}

  A typical simulation volume contains four pores in a monoclinic unit cell,
  the smallest unit cell that maintains hexagonal symmetry when extended 
  periodically.
  \begin{itemize}
    \item Each pore is made of twenty stacked monomer layers with periodic 
    continuity in the z direction, avoiding any edge effects and creating an 
    infinite length pore ideal for studying transport.
    \item A small number of layers is preferred in order to reduce computational
    cost and to allow us to look at longer timescales.
    \item Ultimately, we chose to build a system with 20 monomer layers in each pore
    in order to obtain sufficient resolution when simulating X-ray diffraction patterns.
    This point will be explained in more detail later.
    %MRS: you should give the reasons in the same place you describe the choice, but the supporting data would probably be better in supporting information 
  \end{itemize}

@@

  %MRS Breaking into more structure is good. Short sentences, only 3-5 sentences per paragraph.
  %MRS: really, this the core of the 

@@

    %MRS: initial distance between pores -- we set the initial, and let it find where it wants to be
    %MRS: Or is this the initial data we COMPARE to? Be more specific about the use of these numbers. The use of the data needs to be clarified, since it's main effort here. 

@@

    %MRS: somewhere, should explain there's a large dependence of (meta)stable structures based on this initial distance.  It's sort of important to put somewhere. 

@@

    a perfect hexagonal array. Only 4 are independent  
    %BJC: small figure here for clarity? supplemental info?
    %MRS: probably supplemental. 

@@

    %MRS: initial layer spacing.  

@@

    \item The pattern shows reflections corresponding to features spaced 3.7 \angstrom~apart.

@@

    %MRS: pore radius is a different category isn't it? Is this an input piece of data?
    % should be put in a different category.

@@

    %MRS: point out this is one of the things that atomistic simulation can actually do very well - 
    % provide a clear picture of a nanoscopic environment (the questions is whether it's 
    % providing the _right_ clear picture).

@@

    %MRS: OK, this is a variable again that we need to set. 

@@

    its $\approx$ 5 \angstrom~equilibrium stacking distance ~\cite{sinnokrot_estimates_2002}.

@@

    %MRS: hard to say. It's certainly a big switch from things that are relatively straightforward to things that require 
    % a fair amount of information, so I think it belongs in it's own section -- so far, you're just laying out the approach.  This is what we fix, this is what we leave as a variable.  The analysis probably belongs later.

@@

  An equilibration scheme with position restraints placed on aromatic rings
  %MRS: 
  %prevents 
  is required to prevent
  unrealistic jumps during early equilibration steps.
  %MRS: should be clearer what you mean by ``unrealistic jumps''.  Hard to visualize.
  \begin{itemize}
    \item Restraints fix monomer head groups in the sandwiched or parallel-displaced
    configurations while allowing monomer tails to settle.
    \item Doing so also mitigates system dependence on initial monomer configuration.
    \item Restrained equilibrations are run in the NVT ensemble.
    \item Every 50 ps, we reduce the force constants by the square root of its 
    previous value, starting from 1e6 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}.
    \item Once the force constant is below 10 KJ mol\textsuperscript{-1} 
    nm\textsuperscript{-2}, the restraints are slowly released until there is no more 
    restraining potential.  %BJC: I can reference an equilibration script that can be released with the supplemental info or something
    \item The resulting unrestrained structure is allowed to equilibrate in the NPT
    ensemble for 400 - 500 ns.
   %MRS: we should release as many scripts as is feasible, can be in a github repository.
   %MRS: You've described two equilibration procedures (or two varieties of the same one?) - need to be crystal clear to the reader as to which is used where.
  \end{itemize}

  %BJC: the following paragraph will be replaced with something that Joe writes
  %MRS: sounds good.
  Simulated X-ray diffraction patterns were generated based on atomic
  coordinates for a direct experimental comparison.
  \begin{itemize}
    \item All atomic coordinates were simulated as gaussian spheres of electron
    density corresponding to each atom's atomic number.
    \item A three dimensional fourier transform (FT) of the array of electron 
    density results in a three dimensional structure factor which represents
    the unit cell in reciprocal space.
    \item We perform an angular average of the structure factor about the 
    z axis to generate a 2D cross section close to what one would see 
    experimentally.
    \item We matched experimental 2D WAXS patterns by iterative improvement
    of our choice of initial structure and equilibration procedure.
  \end{itemize}

  \begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwiched.png}
		\caption{}\label{fig:sandwiched}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{PD.png}
		\caption{}\label{fig:pd}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Tshaped.png}
		\caption{}\label{fig:tshaped}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwichedlayers.png}
		\caption{}\label{fig:sandwichedlayers}
	\end{subfigure}
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offsetlayers.png}
		\caption{}\label{fig:offsetlayers}
	\end{subfigure}
	\caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom apart. (b) Parallel-Displaced benzene dimers stack
	3.4 \angstrom vertically and 1.6 \angstrom horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom apart. 
	(d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
	configuration }\label{fig:stacking}
  \end{figure}

  Ionic conductivity was calculated using two different methods for
  robustness.
  \begin{itemize}
    \item The Nernst-Einstein relation relates the DC ionic conductivity to 
    ion diffusivity, $D$, concentration, $C$, ion charge, $q$, the boltzmann 
    constant, $k_b$, and temperature, $T$: $$\sigma = \dfrac{q^2CD}{k_b T}$$  %BJC: need citation
    \item Sodium ion diffusion coefficients were found by calculating the slope
    of the linear region of the mean square displacement curve as indicated by
    the einstein relation \cite{einstein_investigations_1956}.]
    %MRS: state how you decided which was the linear region.  
    \item Ion concentration was measured with respect to the entire unit cell. 
    %BJC: I don't think this needs to be said
    %MRS: probably - people might think of conduction just occurring in the pore, so clarity is good. Could potentially have a figure illustrating the two ways of calculating conductance?  
    \item The second method, termed the 'Collective Diffusion' model, measures 
    the movement of the collective variable, Q, which is defined as the amount
    of charge transfer through the system.
    \item The diffusion coefficient of Q, $D_Q$, can be calculated using the 
    einstein relation.
    %MRS: might need a bit more mathematical description of what is done here. For example explicitly stating that the D is 
    % the diffusion coefficient of the variable D, which is the center of the charge (I think?)
    \item The conductance, $\gamma$ of the system can be calculated as:
    $$ \gamma = \dfrac{D_Q}{k_b T} $$ Conversion to ionic conductivity is
    achieved by multiplying by channel length and dividing by the membrane
    cross sectional area.
    \item A full derivation of the model can be accessed elsewhere \cite{liu_collective_2013}.
    %MRS: still want to state it clearly.   
  \end{itemize}

  Using an equilibrated structure, a crosslinking procedure was performed
  in order to better parallel synthetic procedures. 
  \begin{itemize}
    \item The purpose of crosslinking is to maintain macroscopic alignment of 
    the crystalline domains, ensuring aligned, hexagonally packed pores.
    \item For that reason, we are not concerned with replicating the kinetics 
    of the reaction, but instead emphasize the consistency of the final structure
    with experimental structural data.
    \item The algorithm was developed based on the known reaction mechanism.
    \item Crosslinking of this system is a free radical polymerization (FRP)
    taking place between terminal vinyl groups present on each of the three
    monomer tails.
    \item FRPs require an initiator which bonds to the system, meaning new atoms
    were introduced into the system.
    \item For simplicity, the initiator was simulated as hydrogen and made present 
    in the simulation by including them in all possible bonding positions as dummy atoms.
    \item The crosslinking procedure is carried out iteratively.
    \item During each iteration, bonding carbon atoms are chosen based on a distance cut-off.
    \item The topology is updated with new bonds and dummy hydrogen atoms are 
    changed to appropriate hydrogen types. 
    \item Head-to-tail addition was the only propagation mode considered due to 
    its dominance the real system.
    \item Direction of attack was not considered because the resultant mixture 
    is racemic.
    %BJC: The following items belongs in results/discussion
    %MRS: probably. 
    \item The resulting crosslinked structure has an even distribution of
    crosslinks between monomer tails of the same monomer, monomers stacked on
    top of each other and monomers in other pores, including across periodic
    boundaries.
    \item The pore spacing shrinks by $\approx$ 1 \angstrom and stays 
    constant under a range of simulation conditions.
  \end{itemize}

@@

  To discern the composition of the monomer layers, we ran simulations of 
  systems created with 4 - 8 monomers per layer.
  \begin{itemize}
  	\item Both the sandwiched and parallel displaced configurations were tested.
	\item All systems remained stable for at least 50 ns.
        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
        %MRS: are they all equally stable? I though you had some additional information on this. Are you saving it for later?  
        %MRS: remind people where the uncertainty comes from.

	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
	Systems built with 5 monomers in each layer equilibrate to a pore spacing
	that is most consistent with the experimental value of 4.12 nm derived from
	SAXS measurements (Figure~\ref{fig:SAXS}).
	\item We verified that the system stays partitioned into layers by plotting 
	pair correlation functions calculated between aromatic rings along the length
	of the pores (Fig~\ref{fig:zdf}).
        %MRS: explain how that conclusion was reached (perioic with period X, minima was Y percent lower than mean, maxima was Y percent higher).
	\item The remainder of this discussion will focus on the analysis of systems
	built with 5 monomers per layer. 
  \end{itemize}
